Primary analyses

### 2025-04-24 analysis/primary_analyses.qmd
add table 1

@@

```{r}
results <- saveRDS(
  object = list(
    table2 = table2, table3 = table3, table4 = table4
    ), 
  file = "../results/results.rds"
)
```

>>>>

## Descriptive statistics

```{r}
dat_desc <- bind_rows(
  dat_poly |> select(Geschlecht, Bildung, Muttersprache, Alter_realW) |> mutate(categories = "6 categories"),
  dat_dich |> select(Geschlecht, Bildung, Muttersprache, Alter_realW) |> mutate(categories = "2 categories")
)
# dat_desc |> group_by(categories, Geschlecht) |>
#   summarize(N = n()) |> mutate(perc = N / sum(N))
# dat_desc |> group_by(categories, Bildung) |>
#   summarize(N = n()) |> mutate(perc = N / sum(N))
# dat_desc |> group_by(categories, Muttersprache) |>
#   summarize(N = n()) |> mutate(perc = N / sum(N))
# dat_desc |> group_by(categories) |>
#   summarize(MD = median(Alter_realW), SD = sd(Alter_realW), N = n())

table1 <- dat_desc |>
  mutate(Geschlecht = factor(Geschlecht), 
    Bildung = factor(Bildung), 
    Muttersprache = factor(Muttersprache)) |>
  flextable::summarizor(by = "categories") |>
  flextable::as_flextable() |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table1
```

@@

```{r}
results <- saveRDS(
  object = list(
    table1 = table1, table2 = table2, table3 = table3, table4 = table4
    ), 
  file = "../results/results.rds"
)
```
